Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-09-12 latex/paper.tex
[ADD] limitation on benchmark application used.

>>>>

\HL{
	Due to the limited amount of benchmarks available to evaluate the performance
    of neuroimaging applications, we use our collection of applications.
    Multiple studies using their own applications make it harder to compare
    their results.
    Further efforts would be needed to create a credible and in-depth performance
    benchmark specific to the neuroimaging field.
}
